% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
%\usepackage[osf]{xagaramon}

% Set your name here
\def\name{Andrea Cadeddu }

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Software Development, Software Engineering, Software Architecture},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large\sffamily\bfseries}
\subsectionfont{\rmfamily\mdseries\itshape\large\sffamily}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \bf \name}

\vspace{0.25in}
{\Large \bf \sffamily Full-Stack Engineer, Developer, Architect and Scientist}
% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  1209 Elmwood\\
Evanston, IL 60202
  USA \\
  Date of Birth: October 21, 1982 \\
  Citizenship: Italy\\
  Status: EB-2 (green-card)
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Mobile: +1 787 210 5525\\
  Email: \href{mailto:cadedduan@gmail.com}{\tt cadedduan@gmail.com} \\
  \textit{Other Languages: (\href{http://en.wikipedia.org/wiki/Common_European_Framework_of_Reference_for_Languages}{\tt CEFR} )} 

Spanish C1,
English C2, 
French C1,
Catalan A2.

\end{minipage}

\section*{Current Position}

\begin{itemize}
\item Principal Software Engineer, Roomit (CWT), since April 2019. 

\textit{Team lead for real time search Personalization, training and management, project ideation, planning and architecture, development.}

\end{itemize}
\section*{Education}

\begin{itemize}

  \item  Ph.D. Physical Chemistry, Institut de Science et d'Ing\'enierie Supramol\'eculaires (\href{http://www-isis.u-strasbg.fr/}{\texttt{ISIS}}), Universit\'e de Strasbourg , 17 December 2012.

  \item  M.Sc Material Science, University of Cagliari , 2008.

  \item B.Sc Material Science University of Milan Bicocca, 2006.
  
\end{itemize}


\section*{Certificates}
\begin{itemize}
  \item  AWS Certified DevOPS Engineer - Professional
  \item  AWS Certified Developer - Associate
  \item  AWS Solution Architect - Associate
\end{itemize}


\section*{Skills}

\begin{itemize}
  \item  AWS, Serverless, JavaScript, Python, Java, Html5, CSS, Node, Angular, React, Vagrant, Puppet, Ansible, Docker, Kubernetes, Adobe AEM/CQ. some Clojure, some Haskell, some Go.
\end{itemize}

\section*{Research Fields}
Chemistry as a Natural Language, Machine Learning, Chemical Networks, Nanochemistry, Scanning Tunneling Microscopy, Physical Chemistry, Molecular Dynamics;


\section*{Recent Professional Activities}

\begin{itemize}
% 
\item Senior Software Engineer, Roomit (CWT),  April 2018 - April 2019. 
\textit{Training, project ideation, planning and architecture, development. Main product: real time personalization of hotel search services}

\item \href{http://www.turinggroup.com}{Server Central - Turing Group} - Director Software Development,  Chicago  IL, August 2017 - April 2018 
\textit{Responsible for Client relationship, team lead, training and management, project ideation, planning and architecture, development. Aws serverless and event-based streaming architectures}

\item \href{http://www.turinggroup.com}{Server Central - Turing Group} - Software Architect,  Chicago  IL, April 2016 - August 2017 

\textit{Responsible for Client relationship, project ideation, development and training.  AWS architectures, HIPAA EMR software}
\item \href{http://www.hyatt.com}{Hyatt.com} -  Full Stack Developer, Hyatt corporate office,  Chicago  IL, April 2014 - April 2016. 
\item \href{http://www.chematica.net}{Chematica} - Lead Software Engineer and Post Doctoral Fellow , Northwestern University, Non Equilibrium Research Center, Evanston IL, USA. February 2013 - April 2014.

% 
\end{itemize}
\section*{Scientific Publications}
\begin {itemize}
\item       \textit{Atomically Precise Prediction of 2D Self-Assembly of Weakly Bonded Nanostructures: STM Insight into Concentration-Dependent Architectures}. Small 2015.
\item       \textit{Organic chemistry as a language and the implications of chemical linguistics for structural and retrosynthetic analyses}. Angewandte Chemie, Volume 126, Issue 31, pages 8246-8250, July 28, 2014
\item 	    \textit{Concentration Dependent Supramolecular Engineering of H-bonded Nanostructures at Surfaces: Predicting Self-assembly in 2D}. Journal of the American Chemical Society 2013. doi:10.1021/ja4002025.
\item  \textit{Modulating the self-assembly of rigid clicked dendrimers at the solid-liquid interface}, Chemical Communications, 2011, 47, 10578-10580.
\item  \textit{
Self-templating 2D supramolecular networks: a new avenue to reach control over a bilayer formation}, Nanoscale, 2011, 3, 4125-4129.
\end{itemize}

\section* {Other Publications}
\begin {itemize}
\item case study for IoT lockers: \href{https://www.servercentral.com/case-study-florence/}{\tt {servercentral.com/case-study-florence }}
\item case study for Metra: \href{https://www.servercentral.com/case-study-metra/}{\tt {servercentral.com/case-study-metra/}}
\end {itemize}



% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
